\documentclass[12pt,twoside,reqno]{amsart}
%\documentclass[12pt]{article}

\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{amsthm, amsmath, amscd, amssymb,centernot}
\usepackage[all]{xy}
\usepackage[T1]{fontenc}
\usepackage[left=2.5cm,top=2.5cm,bottom=3cm,right=2.5cm]{geometry}
\usepackage{amsthm, amsmath, amscd, amssymb,centernot}
\usepackage{comment}
\setlength{\headheight}{15.2pt}
\setlength\parskip{.1in}
\setlength\parindent{0.2in}

%\usepackage{tikz}https://www.overleaf.com/project/642e283246ec4730b8bdf398
\usepackage{csquotes}

\newcommand{\s}{\varepsilon}

\numberwithin{equation}{section}
\newtheorem{theorem}{Theorem}[section]
\newtheorem*{theorem*}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{definition}
\newtheorem{question}[theorem]{Question}



\begin{document}
\title{Response to Reviewer}
\begin{description}
\item[Paper ID]  GMJ 231005-Subramaniam

\item [Title] Seshadri Constants of Curve Configurations on Surfaces
\item [Authors] Krishna Hanumanthu, Praveen Roy and Aditya Subramaniam
\end{description}

We thank the referee for carefully reading the manuscript and suggesting 
many useful changes including a valuable suggestion to remove the hypothesis that all the curves in $\mathcal{C}$ are linearly equivalent to a fixed divisor. We were able to do this and our main theorem now (Theorem 2.2 in the new version) is a more general result without the old assumption. 

We also thank the referee for pointing out an error in  Assumption 2.1 which leads to 
ambiguities at several places. We fixed this error by assuming that the arrangement is connected. 

We  agree with the referee that Example 2.22 (in the new version)  can be shortened and it is better to  
focus solely on the computation of Seshadri constants. 

All these suggestions substantially improved the paper and we are grateful to the referee for them. 

Below we describe in detail the changes made to the manuscript based on the referee's comments. 
%We have made all these changes, and we hope that after making these changes, the paper has becomes more accessible for the readers and its overall quality has improved considerably.  Following are somewhat detailed explanation of changes that we have made on the basis of the report. \\
\begin{itemize}

\item As the referee mentioned correctly, the proof of the main theorem in the original version did not really need the assumption that all the curves are linearly equivalent to a fixed divisor. We removed this hypothesis and the hypothesis that $\mathcal{C}$ is a star arrangement and re-wrote the proof in the more general setting. The earlier results were retained as corollaries. 

We also modified some of the questions we asked to fit the more general setting of the new version. 



\item Following the referee's suggestion, we included the assumption that the arrangement $\mathcal{C}$ is \textit{connected} throughout. 
This assumption is added in Definition 1.2 itself where transversal arrangements are defined. 

%We also added a remark immediately after Assumption 2.1 mentioning that the connectedness assumption implies that $C_i \cdot C_j > 0$ for all $i,j$.

\item We  removed the unnecessary assumption that all the curves do not meet at any point. Referee correctly noted that this is not necessary for the main results. 

We only needed this assumption while computing the configurational Seshadri constants in  Theorems 2.18, 2.19 and 2.21 (in the new version) . We therefore added the required assumption in the statements of Theorem 2.18 and Theorem 2.21. (In Theorem 2.19, the hypotheses of Theorem 2.18 are assumed.)

%agree with the referee about the problem in our way of using the Assumption 2.1. While writing the paper, we always had in mind the \textbf{connectedness of the arrangement}, 
%which we somehow missed to incorporate in the Assumption 2.1. We have now made it clear in the manuscript. \\
%\item Note that, now we don't require the semi-ampleness of divisor $A$ for $C_i^2$ to be positive, and it follows 
%from the connectedness of the arrangement. 

%Additionally, we would prefer to retain the second part of Assumption 2.1, as removing that requires 
%significant amount of additional work which we are currently not inclined to pursue. In-fact even the statement of Theorem 2.5 will change, if we remove the second assumption. 
%By the phrase `curves are linearly equivalent to a fixed divisor $A$', we mean that, $C_i \in |A|$ (linear system of $A$) for all $i$. \\

\item We  revised Example 2.22 (in the new version) considerably. We shortened it to focus solely on the computation of the Seshadri constant.
\end{itemize}


%We once again thank the referee for a quick review, we hope that we addressed all the concerns of the referee regarding this manuscript.


\end{document}